Biotic interactions structure zooplankton metacommunity dynamics following a summer heatwave

### 2024-03-07 writing/Manuscript.Rmd
moved statement of authorship and data accessibility statement to after acknowledgements

### Data Accessibility Statement
All code and data for this study are available on https://github.com/plthompson/Zoop_metacom_exp_2018 and are archived on Dryad - .

@@

>>>>

@@

### Data Accessibility Statement
All code and data for this study are available on https://github.com/plthompson/Zoop_metacom_exp_2018 and are archived on Dryad - doi to come.
